State whether the following statements are true false. Justify your answer
\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
\item If $(-4,3)\text{ and }(4,3)$ are two vertices of an equilateral triangle. Find the coordinates of the third vertex, given that the origin lies in the interior of the triangle. 
\item $\vec{A} (6,1),\vec{B}(8,2) \text{ and } \vec{C}(9,4)$ are three vertices of a parallelogram ABCD. If $\vec{C}$ is the midpoint of DC find the area of $\triangle ADE$
\item The points $\vec{A} (x_1,y_1),\vec{B}(x_2,y_2)\text{ and } \vec{C} (x_3,y_3) $ are the vertices of $\triangle ABC$
	\begin{enumerate}	
		\item The median from $\vec{A}$ meets BC at $\vec{D}$ find the coordinates of the point $\vec{D}$
		\item Find the coordinates of the point $\vec{p}$ on AD such that AP.PD=2
\item Find the coordinates of points $\vec{Q}$ and $\vec{R}$ an medians BE and CF respectively such that BQ:QE=2:1 and CR:RF=2:1
\item What are the coordinates of the centroid of the triangle ABC
	\end{enumerate}
\item If the points  $\vec{A}(1,-2), \vec{B}(2,3) , \vec{C}(a,2)\text{ and }\vec{D} (-4-3)$ form parallelogram, find the value of $a$ and height of the parallelogram taking AB as base.
\item Ayush starts walking from his house to office. Instead of going to the office directly, he goes to a bank first, from there to his daughter school and then reaches the office what is the extra distance travelled by Ayush in reaching his office? (Assume that all distanes covered are in straight lines). If the house is situated at $(2,4)$, bank at $(5,8)$, school at $(13,14)$ and office at $(13,26)$ and coordinates are in km.

	\end{enumerate}

