
\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]

\item In traingles ABC and PQR, $ \angle{A} = \angle{Q} $ and $ \angle{B} = \angle{R} $.Which side of $ \triangle{PQR} $ should be equal to side AB of $ \triangle{ABC} $ so that the two triangles are congruent?Give reason for your answer.

\item In triangles ABC and PQR, $ \angle{A} = \angle{Q} $ and $ \angle{B} = \angle{R} $.Which side of $ \triangle{PQR} $should be equal to side BC of $ \triangle{ABC} $ so that the two triangles are congruent?Give reason for your answer.

\item "If two sides and an angle of one triangle are equal to two sides and an angle ofanother triangle,then two triangles must be congruent."Is the statement true?Why?

\item "If two angles and a side one triangle are equal to two angles and a side of another triangle,then the two triangles must be congruent."Is the statement true?Why?

\item Is it possible to construct a triangle with lengths of its sides as 4 cm, 3 cm and 7 cm?Give reason for your answer.

\item It is given that $ \triangle{ABC} \cong \triangle{RPQ} $.Is it true to say that BC = QR?Why?

\item If $ \triangle{PQR} \cong \triangle{EDF} $,then is it true to say that PR = EF?Give reason for your answer.

\item In $ \triangle{PQR} $,$ \angle{P} = 70\degree $ and $ \angle{R} = 30\degree $.Which side of the triangle is the longest?Give reason for your answer.

\item AD is a median of the triangle ABC.Is it true that AB + BC + CA $ > $ 2AD?Give reason for your answer.

\item M is a point on side BC of a triangle ABC such that AM is the bisector of $ \angle{BAC} $.Is it true to say that perimeter of the triangle is greater than 2AM?Give reason for your answer.

\item Is it possible to construct a triangle with lengths of its sides as 9 cm, 7 cm and 17 cm?Give reason for your answer.

\item Is it possible to cosntruct a triangle with lengths of its sides as 8 cm, 7 cm and 4 cm?Give reason for your answer.


\end{enumerate}
