\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}
\item Check whether$(5,-2),(6,4)$ and $(7,-2)$ are the vertices of an isosceles triangle.
\item Name the type of quadrilateral formed, if any, by the following points,and give reasons for your answer
\begin{enumerate}
\item $(-1,-2),(1,0),(-1,2),(-3,0)$
\item $(-3,5),(-3,1),(0,3),(-1,-4)$
\item $(4,5),(7,6),(4,3),(1,2)$
\end{enumerate}
\solution
		\input{chapters/10/7/1/6/inner.tex}
\item Find the projection of the vector $\hat{i}-\hat{j}$ on the vector $\hat{i}+\hat{j}$.
	\\
		\input{chapters/12/10/3/3/inner.tex}
\item Find the projection of the vector $\hat{i}+3\hat{j}+7\hat{k}$ on the vector $7\hat{i}-\hat{j}+8\hat{k}$.
	\\
	\solution
		\input{chapters/12/10/3/4/inner.tex}
\item Show that each of the given three vectors is a unit vector: 
 $\frac{1}{7}(2\hat{i}+3\hat{j}+6\hat{k}),\frac{1}{7}(3\hat{i}-6\hat{j}+2\hat{k}),\frac{1}{7}(6\hat{i}+2\hat{j}-3\hat{k}$)
Also,show that they are mutually perpendicular to each other.
	\\
	\solution
		\input{chapters/12/10/3/5/inner.tex}
\item If $\overrightarrow {a}=2\hat{i}+2\hat{j}3\hat{k},\overrightarrow {b}=\hat{-i}+2\hat{j}+\hat{k}$ and $\overrightarrow {c}=3\hat{i}+\hat{j}$ are such that $\overrightarrow {a}+\lambda\overrightarrow {b}$ is perpendicular to $\overrightarrow {c}$,then find the value of $\lambda$.
	\\
		\input{chapters/12/10/3/10/inner.tex}
\item Show that $\abs {\overrightarrow {a}}\overrightarrow {b}+\abs{\overrightarrow {b}}\overrightarrow {a}$ is perpendicular to $\abs{\overrightarrow {a}} \overrightarrow {b}-\abs{\overrightarrow {b}} \overrightarrow {a}$, for any two nonzero vectors $\overrightarrow {a}$ and $\overrightarrow {b}$.
	\\
	\solution
		\input{chapters/12/10/3/11/inner.tex}
\item If $\overrightarrow {a}.\overrightarrow {a}$=0 and $\overrightarrow {a}.\overrightarrow {b}$=0, then what can be conculded about the vector $\overrightarrow {b}$?
\item If $\overrightarrow {a},\overrightarrow {b},\overrightarrow {c}$ are unit vectors such that $\overrightarrow {a}+\overrightarrow {b}+\overrightarrow {c}=\overrightarrow {0}$, find the value of $\overrightarrow {a}.\overrightarrow {b}+\overrightarrow {b}.\overrightarrow {c}+\overrightarrow {c}.\overrightarrow {a}$.
	\\
	\solution
		\input{chapters/12/10/3/13/norm.tex}
\item If either vector $\overrightarrow {a}=0$ or $\overrightarrow {b}=0$, then $\overrightarrow {a}.\overrightarrow {b}$=0. But the converse need not be true. Justify your answer with an example.
	\\
	\solution
		\input{chapters/12/10/3/14/inner.tex}
\item Show that the vectors $2\hat{i}-\hat{j}+\hat{k},\hat{i}-3\hat{j}-5\hat{k}$ and  $3\hat{i}-4\hat{j}-4\hat{k}$ from the vertices of a right angled triangle.
	\\
	\solution
		\input{chapters/12/10/3/17/inner.tex}
\item Show that the points A, B and C with position vectors,$\vec{a}=3\hat{i}-4\hat{j}-4\hat{k}$,$\vec{b}=2\hat{i}-\hat{j}+\hat{k}$ and $\vec{c}=\hat{i}-3\hat{j}-5\hat{k}$, respectively form the vertices of a right angled
triangle.
\\
\solution
		\input{chapters/12/10/2/17/inner.tex}
\item Let $\vec{a}=\hat{i}+4\hat{j}+2\hat{k}$,$\vec{b}=3\hat{i}-2\hat{j}+7\hat{k}$ and $\vec{c}=2\hat{i}-\hat{j}+4\hat{k}$.Find a vector $\vec{d}$ which is perpendicular to both $\vec{a}$ and $\vec{b}$,and $\vec{c}.\vec{d}$=15.\\
	\solution
		\input{chapters/12/10/5/12/equation.tex}
\item Prove that $(\vec{a}+\vec{b}).(\vec{a}+\vec{b})$=$|{\vec{a}}|^2+|{\vec{b}}|^2$,if and only if $\vec{a},\vec{b}$ are perpendicular, given $\vec{a}\neq\vec{0}$,$\vec{b}\neq\vec{0}$.\\
	\solution
		\input{chapters/12/10/5/15/inner.tex}
\item $ABCD$ is a rectangle formed by the points $\vec{A}(–1, –1), \vec{B}(– 1, 4), \vec{C}(5, 4)$  and  $\vec{D}(5, – 1)$. $\vec{P}, \vec{Q}, \vec{R}$ and $\vec{S}$ are the mid-points of $AB, BC, CD$ and $DA$ respectively. Is the quadrilateral $PQRS$ a square? a rectangle? or a rhombus? Justify your answer.
	\\
	\input{chapters/10/7/4/8/inner.tex}
\item Without using the Baudhayana theorem, show that the points $(4,4),(3,5)$ and $(-1,-1)$ are the vertices of a right angled triangle.
\label{chapters/11/10/1/6}
\input{chapters/11/10/1/6/matrix.tex}
\item The line through the points $(h, 3)$ and $(4, 1)$ intersects the line $7x- 9y- 19= 0$ at right angle. Find the value of $h$.
\label{chapters/11/10/3/10}
\\
\solution
\input{chapters/11/10/3/10/line.tex}
\item In the following cases, determine whether the given planes are parallel or perpendicular, and in case they are neither, find the angles between them.
\begin{enumerate}
\item $7x + 5y + 6z + 30 = 0$ and $3x – y – 10z + 4 = 0$
\item $2x + y + 3z – 2 = 0$ and $x – 2y + 5 = 0$
\item $2x – 2y + 4z + 5 = 0$ and $3x – 3y + 6z – 1 = 0$
\item $2x – y + 3z – 1 = 0$ and $2x – y + 3z + 3 = 0$
\item $4x + 8y + z – 8 = 0$ and $y + z – 4 = 0$
\end{enumerate}
    \solution
		\input{chapters/12/11/3/13/inner.tex}
		\item 
 Show that the line joining the origin to the point $(2, 1, 1)$ is perpendicular to the
line determined by the points $(3, 5, – 1), (4, 3, – 1)$.
\\
    \solution
		\input{chapters/12/11/4/1/inner.tex}
	\item  If $l_1, m_1,n_1 \text{ and } l_2,m_2,n_2$ are the direction cosines of two mutually perpendicular lines, show that the direction cosines of the line perpendicular to both these are  $m_1n_2-m_2n_1,n_1l_2-n_2l_1,l_1m_2-l_2m_1$.
\\
    \solution
		\input{chapters/12/11/4/2/inner.tex}
	\item If the lines $\frac{x-1}{-3} = \frac{y-2}{2k} = \frac{z-3}{2}$ and  $\frac{x-1}{3k} = \frac{y-1}{1} = \frac{z-6}{-5}$ are perpendicular, find the value of k.\\
    \solution
		\input{chapters/12/11/4/6/inner.tex}
\item If $\vec{a},\vec{b},\vec{c}$ are mutually perpendicular vectors of equal magnitudes, show that the vector $\vec{c}.\vec{d}$=15 is equally inclined to $\vec{a},\vec{b}$ and $\vec{c}$.\\
\end{enumerate}
