
\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
\item An arch is in the form of a parabola with its axis vertical. The arch is 10m high and 5m wide at the base. How wide is it 2m from the vertex of the parabola?
\label{chapters/11/11/5/2}
\input{chapters/11/11/5/2/conic.tex}
\item 
    \item Find the area of the triangle formed by the lines joining the vertex 
    of the parabola 
    \begin{align}
        x^2 = 12y
        \label{eq:chapters/11/11/5/6/parabola}
    \end{align}
    to the ends of its latus rectum.
\label{chapters/11/11/5/6}
\input{chapters/11/11/5/6/parab.tex}
\item An equilateral triangle is inscribed in the parabola $y^{2} = 4ax$,where one vertex is at the vertex of the parabola. Find the length of the side of the triangle.
\label{chapters/11/11/5/8}
\input{chapters/11/11/5/8/parab.tex}
\end{enumerate}
In the each of the following Exercises, find the coordinates of the focus, axis of the parabola, the equation of the directrix and the length of the latus rectum.
\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi,resume*]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}

\item $y^2$=12x 
\label{chapters/11/11/2/1}
\\
\solution
\input{chapters/11/11/2/1/parab.tex}


\item $x^2$=6y 
\\
\solution
\input{chapters/11/11/2/2/parab.tex}
\item Find the coordinates of the focus, axis of the
parabola, the equation of the directrix and the length of the latus rectum of $y^2 = –8x$
\\
\solution
\input{chapters/11/11/2/3/parab.tex}
\item $y^2$=-8x

\item $x^2$=-16y
\\
\solution
\input{chapters/11/11/2/4/parab.tex}

\item $y^2$=10x  

\item $x^2$=-9y  
\end{enumerate}

Each of the Exercises, find the equation of the parabola, that satisfies the given conditions.

\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi,resume*]
\item Focus(6,0); directrix x=-6 
\item Focus(0,-3); directrix y=3
\item Vertex(0,0); Focus(3,0)
\item Vertex(0,0); Focus(-2,0) 
\item Vertex(0,0) passing through(2,3) and axis is along x-axis
\item Vertex(0,0) passing through(5,2) symmetric with respect to y-axis
\end{enumerate}
