\documentclass[12pt]{article}
\usepackage{graphicx}
%\documentclass[journal,12pt,twocolumn]{IEEEtran}
\usepackage[none]{hyphenat}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{amsmath}   % for having text in math mode
\usepackage{listings}
\usepackage{gensymb}
\lstset{
  frame=single,
  breaklines=true
}
%New macro definitions
\newcommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\solution}{\noindent \textbf{Solution: }}
\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\let\vec\mathbf

\begin{document}
\begin{center}
\textbf\large{CLASS-12\\CHAPTER-6 \\ Application of Derivatives}
\end{center}

\section*{EXERCISE - 6.3}
\section*{Short Answer (S.A.)}
\begin{enumerate}
\item A spherical ball of salt is dissolving in water in such a manner that the rate of decrease of the volume at any instant is propotional to the surface. prove that the radius is decreasing at a constant rate
\item If the area of a circle increases at a uniform rate.then prove that perimeter varies inversely as the radius.
\item A kite is maving horizontally at a height 151.5 meters .If the speed of kite is 10m/s, how fast is the string being let out when the kite is 250m away from the boy who is flying the kite? The heignt of boy is 1.5m. 
 \item Two men A and B start with velocities V at  the some time from the junction of two roads inclined at 45$\degree$.to each other.If they travel by different roads find the rate at which they are being seperated
\item Find an angle $\theta$,0 $<$0$<$$\frac{\pi}{2}$, which increases twice as fast as its sine.
\item Find the approximate value of $(1,999)^5$
\item Find the approximate value of metal in a hollow spherical shell whose internal and externat radi are 3 cm and 3.0005 cm ,respectively.
\item A man,2m toll,walks at the rate or $1\frac{2}{3}$ m/s towards a street light which is $5\frac{2}{3}$ mabove the ground .At what rate is the tip of his shadow moving ? At what rate is the length of the shadow changing when he is $3\frac{1}{3}$- m from the bag of the light?
\item A swimming pool  is to be drained for cleaning lf L represents the number of litres of water in the pool t seconds after the pool has been plugged off to drain and L=200 $(10-t)^2$ How fast is  the water running out at the end af 5 seconds? what is the average rate ot which the water flows out during the first 5 seconds?
\item The volume of a cube increases at a constant rate. prove that the increase in its surface area varies inversety as the length of the side.
\item x and y are the sides of two squares such that $y=x-x^2.$ Find the rate of change of the area of second square with respect to the area of first square.
\item Find the condition that the curves $2x=y^2$ and 2xy=k intersect orthogonally.
\item prove that the curves xy=4 and $x^2+y^2=8$ touch each other.
\item Find the co-ordinates of the point on the curve $\sqrt{x}+\sqrt{y}$=4 ot which tongent is equally inclined to the oxes.
\item Find the angle of intersection of the curves $y=4-x^2$ and $y=x^2$
\item prove that the curves $y^2=4x$ and $x^2+y^2-6x+1=0$ touch each each other ot the point (1,2).
\item Find the equation of the normal lihes to the cure $3x^2-y^2=8$ which are paralle to the line x+3y=4.
\item At what points on the curve $x^2+y^2-2x-4y+1=0$, the tangents are parallel to the y-axis?
\item show that the line $\frac{x}{a}+\frac{y}{b}=1$ .touches the curve $y=be-\frac{x}{a}$ at the point where the curve intersects the axis of y
\item show that f (x)=2x+cot1x +log $\cot^{-1}(\sqrt{1+x^2}-x)$ is intersects in R
\item show that for a $>$1,f(x)=3 sinx-cosx 2ax+b is decreasing in r.
\item show that f (x) $=\tan ^{-1}(sinx+ cosx)$ isan increasing function in$(0,\frac{\pi}{4})$
\item At what point ,the slope of the curve $y=-x^3+3x^2+9x-27$ is maximum? Also find the maximum slope.
\item prove that f (x)=sinx+$\sqrt{3}$ cosx has maximum value at $x=\frac{\pi}{6}$
	\section*{Long Answer (L.A)}
\item If the sum of the lengths of the hypotenuse and a side of a right angled triangle is given, show that the area of the triangle is maximum when the angle between them is $\frac{\pi}{3}$
\item Find the points of local maximal, local minima and the points of inflection of the function f (x)=$x^5-5x4+5x^2-1$. Also find the corresponding local maximam and local minimum values
\item A telephone company in a town has 500 subscribers on its and collects fixed charges of RS 300/- per subscriber per year. The company proposes to increase the annual subscription and it is belived that fog every increase of Re1/. one subsariber will discontinue the serice. find what increase will bring maximum profit?
\item If the straight line x casoc+y sno oc=P touches the curve $\frac{x^2}{a^2}+\frac{y^2}{b^2}=1$ ,\text{then prove that} $a^2 \cos^{2}\alpha+b^2 \sin^{2}\alpha=P^2$.
\item An open box with square base is to be made of a given quantity of card board of area $c^2$. show that the maiximum volume of the box is $\frac{c^23}{6\sqrt{3}}$cubic units.
\item Find the bimensions of the rectangle of perimeter 36cm which will sweep out a volume as large as possible, when revolved about one of its sides. Also find the maximum voiume.
\item lf the sum of the surface areas of cube and a sphere is constant, what is the ratio of on edge of the cube to the diameter of the sphere when the sum of their volumes is minimum?
\item AB is a diameter of a circle and c is any point on the circle show that the area of $\triangle$ABC is maximum, when it is isosceles,
\item A metal box with a square base and vertical sides is to contain $1024 cm^3$ The material for the top and bottom casts $RS 5/cm^2$ and the material for the sides costs Rs$2.50/cm^2$.Find the least cost of the box.
\item The sum of the surface areas of a rectangular parallelopiped with sides x,2x and $\frac{x}{3}$ and a sphere is given to be constant. prove that the sum of their volumes is minimum, if x is equal to three times the radius of the sphere Also find the minimum value of the sum of their volumes
	\section*{Objective Type Questions}
choose the correct answer from the given four options in each of the following questions 35 to 39 ;
\item The sides of an equilateral triangle are increasing at the rate of 2 cm/sec The rate at which the area increases, when side is 10 cm is
\begin{enumerate}
\item 10$cm^2/s$
\item $\sqrt{3}cm^2/s$
\item 10$\sqrt{3}cm^2/s$
\item $\frac{10}{3}cm^2/s$
\end{enumerate}
\item A ladder, 5 meter long standing on a horizontal floor , leans against a vertical wall.lf the top of the ladder slides downwards ot the rate ot the rate of 10cm/sec then the rate at the rate of 10c/sec the the rate at which the angle between the floor and the ladder is decreasing when lower end of ladder is 2 metres from the wall is  ;
\begin{enumerate}
\item $\frac{1}{10}$ radian/sec
\item $\frac{1}{20}$ redian/sec
\item 20 radian/sec
\item 10 radian/sec
\end{enumerate}
\item The curve y=$x\frac{1}{5}$ has at(0,0)
\begin{enumerate}
\item a vertical tongent(parallel to y-axis)
\item ahorizontal tangent(parallel tox.axis)
\item an oblique tangent
\item an  tangent
\end{enumerate}
 \item The equation of normal to the curve $3x^2-y^2 =8$ which is parallei to the line x+3y=8 is
 \begin{enumerate}
 \item 3x-y=8
 \item 3x+y+8=0
 \item x+3y+8=0
 \item x+3y=0
 \end{enumerate}
 \item If the curve $ay+x^2=7$ and $x^3=y$, cut orthoonally at (1,1) ,then the value of ais
 \begin{enumerate}
 \item 1
 \item 0
 \item -6
 \item 6
 \end{enumerate}
 \item If $y=x^4-10$ and if x changes from 2+01,9a what is the change in y
 \begin{enumerate}
 \item -32
 \item .032
\item 5.68
\item 5.969
\end{enumerate}
\item The equation of tongent to the curvey $(1+x^2) =2-x$, where it crosses x-axis
\begin{enumerate}
\item x+5y=2
\item x-5y=2
\item 5x-y=2
\item 5x+y=2
\end{enumerate}
\item The points at which th tangents to the curve $y=x^3-12x+18$ are parallel to x-axis are:
\begin{enumerate}
\item (2,-2)(-2,-34)
\item (2,34)(-2,0)
\item (0,34),(-2,0)
\item (2,2),(-2,34)
\end{enumerate}
\item The tangent to the curve $y=e^2x$ at the point (0,1) meetsx-axis at:
\begin{enumerate}
\item (0,1)
\item $(\frac{1}{2},0)$
\item (2,0) 
\item(0,2)
\end{enumerate}
\item The slope of tangent to the curve $x=t^2+3t=8 y=2t^2-2t-5$ ot the point (2,-1) is:
\begin{enumerate}
	\item $\frac{22}{7}$
	\item $\frac{6}{7}$
	\item $\frac{-6}{7}$
\item -6
\end{enumerate}
\item The two curves $x^3-3xy^2+2=0$ and $3x^2y-y^3-2=0$ intersect at an angle of
\begin{enumerate}
\item $\frac{\pi}{4}$
\item $\frac{\pi}{3}$
\item $\frac{\pi}{2}$
\item $\frac{\pi}{6}$
\end{enumerate}
\item The interval on which the function f(x)=$2x^3+9x^2+12x-1$ is decreasing is
\begin{enumerate}
\item [-1,8]
\item [-2,-1]
\item [-8,-2]
\item [-1,1]
\end{enumerate}
\item Let the f : $\vec{R}\rightarrow \vec{R}$ be defined by f(x)=2x+ cosx, then f:
\begin{enumerate}
\item has a minimum at x=$\pi$
\item has a maximuum,at x=0
\item is a decreasing function 
\item is an increasing function
\end{enumerate}
\item y=$x(x-3)^2$ decreases for the value of x given by:
\begin{enumerate}
\item 1$<$x
\item x$<$0
\item x$>$0
\item 0$<$x$<$$\frac{3}{2}$
\end{enumerate}
\item The function f(x)=$4sin^3x-6 sin^2x+ 12 sinx+100$ is strictly
\begin{enumerate}
\item increasing in[,$\frac{3}{2}$]
\item decrea sing in[$-\frac{}{2},$]
\item decreasing in[$-\frac{\pi}{2},\frac{\pi}{2}$]
\item decreasing in[0,$\frac{\pi}{2}$]
\end{enumerate}
\item which of the following functions is decreasing an[0,$\frac{pi}{2}$]
\begin{enumerate}
\item $\sin2x$
\item $\tan x$
\item $\cos x$
\item $\cos3x$
\end{enumerate}
\item The function f (x)=$\tan$x-x
\begin{enumerate}
\item always increases 
\item always decreases
\item never increases 
\item sometimes increases and sometimes decreases
\end{enumerate}
\item if x is real ,the minimum value of $x^2-8x+17$is
\begin{enumerate}
\item -1
\item 0
\item 1
\item 2
\end{enumerate}
\item The smallest value of the polynomial $x^3-18x^2+96x$ in [0,9] is
\begin{enumerate}
\item 126
\item 0
\item 135 
\item 160
\end{enumerate}
\item The function f (x)=$2x^3-3x^2-12x+4$ has
\begin{enumerate} 
\item two points of local maximum
\item two points of local minimum
\item one maxima and one minima
\item no marima or minima
\end{enumerate}
\item The maximum volue of sin x casx is 
\begin{enumerate} 
\item $\frac{1}{4}$
\item $\frac{1}{2}$
\item $\sqrt{2}$
\item $2\sqrt{2}$
\end{enumerate}
\item At x =5$\frac{\pi}{6}$ f (x)=2 sin3x+3 cosx
\begin{enumerate} 
\item maximum
\item minimum
\item zero
\item neither maximum nor minimum
\end{enumerate}
\item maximum slope of the curve y=$-x^3+ 3x^2+9x-27$ is
\begin{enumerate} 
\item 0
\item 12
\item 16
\item 32 
\end{enumerate}
\item f (x)=$x^2$ has a stationary point at
\begin{enumerate}
\item x=e
\item x=$\frac{1}{e}$
\item x=1
\item x=$\sqrt{e}$
\end{enumerate}
\item The maximum value of [$\frac{1}{x}$] is
\begin{enumerate}
\item e
\item $e^e$
\item $e^\frac{1}{e}$
\item $\frac{1}{e}^\frac{1}{e}$
\end{enumerate}
Fill in the blanks in each of the following exercisexs 60 to 64:
\item The curves $y=4x^2+2x-8$ and $y=x^3-x+13$ touch each other at the point is \makebox[1cm]{\hrulefill}    
\item The equation of normal to the curvey=tanx at (0,0) is \makebox[1cm]{\hrulefill}
\item The values of a for which the function f (x) sinx-ax+b increases on R are \makebox[1cm]{\hrulefill}
\item The function f (x)=$\frac{2x^2-1}{x^4}$,x$>$0 decreases in the interval is \makebox[1cm]{\hrulefill}
\item The least value of the function f (x)=ax+$\frac{b}{x}$(a$>$0,b$>$0,x$>$0) is \makebox[1cm]{\hrulefill}
\end{enumerate}
\end{document} 
