\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
\item The area of a triangle with vertices $\vec{A}(3, 0), \vec{B}(7, 0) \text{ and } \vec{C}(8, 4)$ is
\begin{enumerate}
\item 14
\item 28
\item 8
\item 6
\end{enumerate}
\item The area of a triangle with vertices $(a,b+c), (b,c+a)\text{ and }(c,a+b)$ is
\begin{enumerate}
\item $(a+b+c)^2$
\item 0
\item a+b+c
\item abc 
\end{enumerate}
\item Find the area of the triangle whose vertices are $(-8,4),(-6,6)\text{ and }(-3,9)$.
\item If $\vec{D}\brak{\frac{-1}{2},\frac{5}{2}},\vec{E}(7,3)\text{ and }\vec{F}\brak{\frac{7}{2},\frac{7}{2}}$ are the midpoints of sides of $\triangle \vec{ABC}$, find the area of the $\triangle \vec{ABC}$.
\item If $\vec{a}+\vec{b}+\vec{c}$=0, show that $\vec{a}\times\vec{b}$=$\vec{b}\times\vec{c}$=$\vec{c}\times\vec{a}$. Interpret the result geometrically?
\item Find the sine of the angle between the vectors $\vec{a}=3\hat{i}+\hat{j}+2\hat{k}$ $\text{ and }$ $\vec{b}=2\hat{i}-2\hat{j}+4\hat{k}$.
\item Using vectors, find the area of $\triangle{ABC}$ with vertices A(1,2,3), B(2,-1,4) and C(4,5,-1).
\item Using vectors, prove that the parallelogram on the same base and between the same parallels are equal in area.
\item If $\vec{a}$, $\vec{b}$, $\vec{c}$ ,determine the vertices of a triangle, show that $\frac{1}{2}$ $\left[\vec{b} \times\vec{c}+\vec{c} \times\vec{a}+\vec{a}\times\vec{b} \right]$ gives the vector area of the trianlge. Hence deduce the condition that the three points $\vec{a},\vec{b},\vec{c},$ are collinear. Also find the unit vector normal to the plane of the triangle.
\item Show that area of the parallelogram whose diagonals are given by $\vec{a}\times\vec{b}$ is $\frac{\abs{\vec{a}\times\vec{b}}}{2}$. Also find the area of the parallelogram whose diagonals are $2\hat{i}-\hat{j}+\hat{k}$ $\text{and}$ $\hat{i}+3\hat{j}-\hat{k}$.

\item The vector from origin to the points A and B are $\vec{a}$ = $2\hat{i}-3\hat{j}+2\hat{k}$ $\text{and}$  $\vec{b}$ = $2\hat{i}+3\hat{j}+\hat{k}$, respectively, then the area of $\triangle {OAB}$ is
	\begin{enumerate}
\item 340 
\item $\sqrt{25}$
\item $\sqrt{229}$
\item $\frac{1}{2}\sqrt{229}$
\end{enumerate}


\item For any vector $\vec{a}$, the value of $(\vec{a}\times\hat{i})^2+(\vec{a}\times\hat{j})^2 + (\vec{a}\times\hat{k})^2$is equal to 
	\begin{enumerate}
\item a 
\item 3a
\item 4a
\item 2a
\end{enumerate}


\item If $\abs{\vec{a}}$=10, $\abs{\vec{b}}=2$ $\text{ and }$  $\vec{a}$, $\vec{b}$=12, then value of $\abs{\vec{a}\times\vec{b}}$ is
	\begin{enumerate}
\item 5 
\item 10 
\item 14 
\item 16
\end{enumerate}

\item If $\vec{a}$ = $\hat{i}+\hat{j}+\hat{k}$ $\text{and}$ $\vec{b}$ = $\hat{j}-\hat{k}$, find a the vector $\vec{c}$ such that $\vec{a}\times\vec{c}$ = $\vec{b}$ $\text{ and}$ $\vec{a}$.$\vec{c}$ = 3.

\item The formula $(\vec{a}+\vec{b})$ = $\vec{a}$+$\vec{b}$ + 2$\vec{a}\times\vec{b}$ is valid for non-zero vectors $\vec{a}$ $\text{and}$ $\vec{b}$.
\item The area of the quadrilateral ABCD, where A$(0,4,1)$, B$(2,3,-1)$, C$(4,5,0)$ and D$(2,6,2)$, is equal to 
\begin{enumerate}
	\item 9 sq. units
	\item 18 sq. units 
	\item 27 sq. units 
	\item 81 sq. units
\end{enumerate}
\item Find the area of region bounded by the triangle whose vertices are (-1, 1), (0, 5) and (3, 2).
\end{enumerate}

